---
title: "Clustering"
author: "Amin Fesharaki"
date: "12/4/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
wine_train <- read.csv(file = "/Users/datascience/Desktop/ADS 502 Data Sets/Website Data Sets/white_wine_training.csv")
wine_test <- read.csv(file = "/Users/datascience/Desktop/ADS 502 Data Sets/Website Data Sets/white_wine_test.csv")
```
## 11. Input and standardize both the training and test data sets.

```{r}
#Separate
X_train <-subset(wine_train, select = c("alcohol", "sugar" ))
X_test <-subset(wine_test, select = c("alcohol", "sugar" ))


#Scale
X_strain = as.data.frame(scale(X_train))
X_stest = as.data.frame(scale(X_test))

colnames(X_strain) <- c("alchohol_z", "sugar_z")
colnames(X_stest) <- c("alchohol_z", "sugar_z")
```
## 12. Run k‐means clustering on the training data set, using two clusters.

```{r}
# Cluster
km_train <- kmeans(X_strain, centers =2)
# Separate Clusters
cluster <- as.factor (km_train$cluster) 
Cluster1train <- X_strain [which(cluster ==1), ]
Cluster2train <- X_strain [which(cluster ==2), ]

```

## 13. Give the mean of each variable within each cluster and use the means to identify a “Dry wines” and a “Sweet wines” cluster.

```{r}
#Cluster 1 Summary
summary(Cluster1train)
```

```{r}
#Cluster 2 Summary
summary(Cluster2train)
```
###Based on the summary statistics for the two clusters, cluster 1 is considered 'Sweet Wines' because it has a signficantly higher sugar mean than cluster 2. Therefore, Cluster 2 is considered 'Dry Wines' (significantly lower sugar mean)


## 14. Validate the clustering results by running k‐means clustering on the test data set, using two clusters, and identifying a “Dry wines” and a “Sweet wines” cluster.
```{r}
# Cluster
km_test <- kmeans(X_stest, centers =2)
# Separate Clusters
cluster1 <- as.factor (km_test$cluster) 
Cluster1test <- X_stest [which(cluster1 ==1), ]
Cluster2test <- X_stest [which(cluster1 ==2), ]

```

```{r}
#Cluster 1 Summary
summary(Cluster1test)
```

```{r}
#Cluster 2 Summary
summary(Cluster2test)
```
###Based on the summary statistics for the two clusters, cluster 1 is considered 'Sweet Wines' because it has a signficantly higher sugar mean than cluster 2. Therefore, Cluster 2 is considered 'Dry Wines' (significantly lower sugar mean)

```{r}
#Validation with difference of means
diff_alc_mean_sweet <- mean(Cluster1train$alchohol_z) - mean(Cluster1test$alchohol_z)
diff_alc_mean_dry <- mean(Cluster2train$alchohol_z) - mean(Cluster2test$alchohol_z) 

diff_sug_mean_sweet <- mean(Cluster1train$sugar_z) - mean(Cluster1test$sugar_z)
diff_sug_mean_dry <- mean(Cluster2train$sugar_z) - mean(Cluster2test$sugar_z) 

cat("The difference in alchohol means for sweet wine", diff_alc_mean_sweet)
cat("\nThe difference in alchohol means for dry wine", diff_alc_mean_dry)
cat("\nThe difference in sugar means for sweet wine", diff_sug_mean_sweet)
cat("\nThe difference in sugar means for dry wine", diff_sug_mean_dry)
```
The data sets are validated. However, the difference of means are relatively small, to further validate the data sets, a two-sample t-test should be used.