---
title: "Naives Bayes Classification"
author: "Amin Fesharaki"
date: "11/14/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(e1071)
```

```{r}
fram_train <- read.csv(file = "/Users/datascience/Desktop/ADS 502 Data Sets/Website Data Sets/framingham_nb_training.csv", sep=',')
fram_test <- read.csv(file = "/Users/datascience/Desktop/ADS 502 Data Sets/Website Data Sets/framingham_nb_training.csv", sep=',')

```

31. Run the Na誰ve Bayes classifier to classify persons as living or dead based on sex and education.

```{r}
nb01 <- naiveBayes(formula = Death ~ Sex + Educ, data = fram_train)
nb01
```

32. Evaluate the Na誰ve Bayes model on the framingham_nb_test dataset.Display theresults in a contingency table. Edit the row and column names of the table to make the table more readable. Include a total row and column.

```{r}
ypred <- predict(object = nb01, newdata = fram_test)

c.pred <- table(fram_test$Death, ypred)
rownames(c.pred) <- c("Actual: Alive", "Actual: Dead")
colnames(c.pred) <- c("Predicted: Alive", "Predicted: Dead")
addmargins(A = c.pred, FUN = list(Total=sum), quiet = TRUE)

```
33. According to your table in the previous exercise, find the following values for the Na誰ve Bayes model: (A) Accuracy, (B) Error Rate
```{r}
# Assigning General Form of Table to matrix values
TN <- c.pred[1,1]
FN <- c.pred[2,1]
FP <- c.pred[1,2]
TP <- c.pred[2,2]


# Accuracy
Acc <- (TN + TP) / (TN + FN + FP + TP)
# Error Rate
Error <- 1 - Acc

cat ("MODEL 2", "\nAccuracy = ", Acc, "\nError =", Error)
```
34. According to your contingency table, find the following values for the Na誰ve Bayesmodel: (A) How often it correctly classifies dead person (B) How often it correctly classifies living persons

(a) The model correctly classifies a dead person 77% (428/550) of the time.
(b) The model correctly classifies an alive person 37% (167/450) of the time.
